### 2025-02-21 acronyms/acronyms.tex
acronyms
acronyms reorg
redi
ece

@@

@@

\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}

@@

@@

@@

\newacronym{pc}{PCAP}{Packet Capture File}
\newacronym{pi}{PI}{Principal Investigator}

@@

\newacronym{usa}{US}{United states}

@@

@@

\newacronym{ece}{ECOE}{Effective Cost of Energy}

@@

%\newacronym{}{}{}
%Add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file/

>>>>

%%%%% acronyms
%
% add \input{$ACRONYM/acronyms} in the preamble, where $ACRONYM is the /path/to/file/
% best practice is to pick a code of 2 or 3 letters
% loosely organized
% just to make it easier to read
%
% \newacronym{}{}{}
%
%%%%%
%
%%%%% universities, education
%
\newacronym{ece}{ECE}{Electrical \& Computer Engineering}
\newacronym{sbe}{SBE}{Idaho State Board of Education}
%
%%%%% national laboratories
%
%%%%% government, societies, ngo 
\newacronym{rdi}{REDI}{Regional Economic Development for Eastern Idaho}
\newacronym{usa}{US}{United States}
%%%%% industry
%%%%% nuclear

@@

%%%%% cybersecurity
\newacronym{hpc}{HPC}{High Performance Computing}
\newacronym{pcp}{PCAP}{Packet Capture File}
%%%%% risk

@@

@@

\newacronym{eco}{ECOE}{Effective Cost of Energy}
\newacronym{pn}{PN}{Petri Net}
%%%%% education
\newacronym{ihe}{IHE}{Institution of Higher Education}

@@

%%%%% proposals
\newacronym{ate}{ATE}{Advanced Technological Education}

@@

@@

@@

\newacronym{pi}{PI}{Principal Invesigator}
%%%%% social science, policy

@@

@@

%%%%%
